Corporate Security Solutions for BYOD.\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-14 MUSES_vs_BYOD_solutions.tex
Comentario para Antares, refers #9
Comment for myself @unintendedbear, for not forgetting it

Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation. They are not being successful in spite of their features. On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}.

As part of its SAFE (Samsung for enterprise) brand, Samsung revealed at the Barcelona Mobile World Congress 2013 the Knox application \cite{Samsung_tool}, which was expected to be available on its last Galaxy smartphone generation. The solution is available since December 2013.
The main feature of this security package is the use of different containers, or environments, for business and personal sides. Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
There will be needed introducing a password to enter into the business side and, once \textit{logged in} this container, no more passwords will be required for the business applications. The applications approved by the company IT department must meet Samsung's security standards and allow single sign-on. A Knox API will also be provided for the company to be capable of accessing over almost 205 predefined IT policies (the SAFE API grows this number to 475). Also, Knox would allow different VPNs for individual apps.
Regarding the information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files. In the same way, the user won't be able to share data between the two environments, e.g. creating separate contact lists so the user cannot send a contact from one side to the other, or if the user copies data to the clipboard in the Knox container, it won't be there in the personal container.

>>>>

Even though these two tools are provided by two different manufacturers, Samsung and Blackberry, they both have in common their situation. They are not being successful in spite of their features. On the one hand, Blackberry sales have been decreasing since 2010 \cite{Blackberry_sales}. 
On the other hand, %Antares needed

With regard to their features, Samsung KNOX, as well as Blackberry Balance, are more focused on the device side, while the solutions mentioned in previous subsections were more centered in being tools for CSOs. This also means that they are not device-independent, as KNOX is only for Samsung devices and Balance is integrated in BlackBerry 10 \cite{Blackberry_tool}.

As part of its SAFE (Samsung for enterprise) brand, Samsung revealed at the Barcelona Mobile World Congress 2013 the Knox application \cite{Samsung_mwc13}, which was expected to be available on its last Galaxy smartphone generation. It was also presented in the same congress in 2014 \cite{Samsung_mwc14}, but... %Completar cuando encuentre la noticia

The solution is available since December 2013.
The main feature of this security package is the use of different containers, or environments, for business and personal sides. Each one even includes its own graphic configuration (wallpapers, colours, and so on), in order to be more easily recognised and distinguished by the user.
There will be needed introducing a password to enter into the business side and, once \textit{logged in} this container, no more passwords will be required for the business applications. The applications approved by the company IT department must meet Samsung's security standards and allow single sign-on. A Knox API will also be provided for the company to be capable of accessing over almost 205 predefined IT policies (the SAFE API grows this number to 475). Also, Knox would allow different VPNs for individual apps.
Regarding the information protection methods, data files saved by applications of each environment are encrypted with AES 256-bit algorithm, in such manner that only the appropriate container can access these files. In the same way, the user won't be able to share data between the two environments, e.g. creating separate contact lists so the user cannot send a contact from one side to the other, or if the user copies data to the clipboard in the Knox container, it won't be there in the personal container.
